Dark matter halo concentrations with a bayesian approach

### 2014-05-26 paper/article.tex
new references and updating procedure

We define the virial radius of a halo, $r_v$, as the boundary of the
spherical volume that encloses an average density of $\Delta_v$ times
the critical density of the Universe. The corresponding mass $M_{v}$
can be thus expressed as $M_{v} = \frac{4\pi}{3}\rho_c\Delta_v r_v^3$.

@@

meaning that the concentration is the only free parameter to
determine the density profile of the halo.

@@

We stop the construction of the integrated mass profile once we arrive
at an average density of $\Delta_h\rho_c$. This radius marks the
virial radius and the virial mass. We divide the total mass enclosed
mass $M_i$ and the radii $r_i$ by these values to obtaine the
dimensionless variables $x_i$ and $m_i$.

@@

\subsection{Mock Halos}
Several halos with known values of $c$ were generated. These halos
were then processed to determine the acurracy of this method. The
number of particles and value of $c$ for each halo were generated
randomly.

@@

>>>>

We define the virial radius of a halo, $r_v$, as the boundary of the
spherical volume that encloses an average density of $\Delta_h$ times
the average density of the Universe. The corresponding mass $M_{v}$,
the virial mass, can be thus expressed as $M_{v} =
\frac{4\pi}{3}\bar{\rho}\Delta_h r_v^3$.

@@

meaning that the concentration is the only free parameter to
determine the density profile of the halo. In Figure
\ref{fig:profiles} we show the family of normalized integrated mass
profiles for different values of the concentration in the range
$1\leq c \leq 20$.

@@

We stop the construction of the integrated mass profile once we arrive
at an average density of $\Delta_h\bar{\rho}$. This radius marks the
virial radius and the virial mass. We divide the total mass enclosed
mass $M_i$ and the radii $r_i$ by these values to obtaine the
dimensionless variables $x_i$ and $m_i$.

@@

\subsection{Mock Halos}

We generate $100$ mock halos with concentration values randomly
placed in the range $1<c<10$. Each one of the halos is generated with
four different total particle numbers: $20$, $200$, $2000$ and $20000$.

The method we use to generate the halos is based on the integrated
mass profile. {\bf Our algorithm works as follows...}

@@

We use data from the MultiDark cosmological volume. This simulation
follows the non-linear evolution of a dark matter density field
sampled with $2048^3$ particles over a cubic box of $1000$ \hMpc on a
side. The data is publicly available, more details about the structure
of the database and the simulations can be found in
\citep{2013AN....334..691R}.

We select a sample of halos in a cubic sub-volumne of $XXX$ \hMpc on a
side. We select first all the halos at $z=0$ detected with a
Friends-of-Friends (FoF) algorithm with masses in the interval $10^{11}\leq
M_{\rm FoF}/\hMsun \leq 10^{15}$. The FoF algorithm ran with a linking
length of $0.17$ times the average interparticle distance. This choice
translates into an overdensity $\Delta_h\sim 700$ that is dependent on
the halo concentration \citep{More2011}.

For each selected halo with the previous procedure we select from the database
all the particles that belong to it. From the particles we follow the
procedure spelled out in Section \ref{sec:method} with $\Delta_h=740$
(corresponding to $200$ times the critical density) to find the
halo concentration. Finally, we store the values obtained for the
virial radius, virial mass and concentration.
